---
title: "Code along crash course: test-driven development"
---

Prerequisite:

1. Participants have been introduced to test-driven development.
2. Participants have forked the `segue` R package repository and created an R studio project form it. See [setup instructions](https://erc-segue.nl/tdd-r-pkg/setup.html).

In groups of 2, including a domain expert and a participant with (some) development experience:

1. Open the test file `tests/testthat/test-segue.R` and write your tests following the template given there. Start with the statements and then write the test code for 1-3 tests.

```{r, eval=FALSE}
# TODO add test data creation code here

# TODO add example tests here

# This is a test
test_that("YOUR STATEMENT HERE", {
	# Test to be added here
})

# Make as many copies of the test block as you need
test_that("YOUR STATEMENT HERE", {
	# Test to be added here
})
```

2. Run the following code to confirm that the tests fail. This is normal.

```{r, eval=FALSE}
devtools::test()
```

3. Open the module file `R/segue.R` and try to implement the function(s) that will help you pass the tests you wrote. Run the tests every time you want to check if the test passes.

```{r, eval=FALSE}
devtools::test()
```

4. Add your name to the `DESCRIPTION` file following this template:

```
Authors@R: c(  # <- Under this seciton
    person("Claudiu", "Forgaci", , "c.forgaci@tudelft.nl", role = c("ctb"),  # <- copy this line
           comment = c(ORCID = "0000-0003-3218-5102")),  # <- and this line
```

5. Commit your changes and push them to GitHub (instructions to be added)

6. Open a Pull Request from your fork (instructions to be added)
